Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-03-27 Multiresolution_framework/ltx/manuscript.tex
added subsection to discussion

The multi-resolution approximation \citep{Mallat1989a} of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(\cdot)$, and the connectivity kernel, $w(\cdot)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(\mathbf{r})$ and a mother wavelet $\psi(\mathbf{r})$. Considering a  one-dimensional field, the static connectivity kernel is decomposed as,
\begin{equation}
 w\left(r\right)=\sum_{l\in \mathbb{Z}}\alpha_{j_0,l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}}, 
\label{eq:KernelExpansion}
\end{equation}
where $\alpha_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$, and $\beta_{j,l}$ are the detail coefficients at different scales $j$, with
\begin{align}
\phi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\phi\left(2^j r-l\right) \label{eq:generalscalingfinction}\\	
\psi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\psi\left(2^j r-l\right).  \label{eq:generalwaveletfinction}
\end{align}
The parameters $j$ and $l$ control the scale (dilation) and translation (spatial shift), respectively. The number of spatial shifts, $l$, is dependent on the scale, $j$, and can be chosen such that the basis functions cover the spatial domain of interest. For example, at scales corresponding to higher spatial frequencies a greater number of wavelets, and thus spatial shifts are required to adequately sample the spatial characteristics of the field. The number of scales depends on the spectral characteristics of the field, where higher spatial frequencies require a more scales. Spatial frequency analysis will be described later in Section~\ref{sec:freq_anal} in greater detail. Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.

@@

By exploiting Eq.~\eqref{eq:BsplineConvolution} and Eq.~\eqref{eq:BsplineInnerProduct}, the integrals in Eq.~\eqref{eq:Lambdax} and Eq.~\eqref{eq:Gammaij} can be computed analytically. In constructing $\boldsymbol\Lambda_{x}$, it is important to note that B-spline scaling and wavelet functions possess the following orthogonality properties \citep{Unser1993}: 
\begin{equation}
  \left\langle \varphi_{m;j_1,l_1}(r),\varphi_{m;j_2,l_2}(r)\right\rangle =0  \quad \mathrm{for} \quad j_1\neq j_2
 \label{eq:MRA-PsiPsiOrthogonality} 
 \end{equation}
 \begin{equation}
  \left\langle N_{m;j_1,l_1}(r),\varphi_{m;j_2,l_2}(r)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2.
 \label{eq:MRA-PhiPsiOrthogonality}
 \end{equation}
Note from Eq.~\eqref{eq:MRA-PsiPsiOrthogonality} B-spline wavelets are semi-orthogonal as they are not orthogonal with respect to translation on a given scale.

@@

It is important to point out there is no doubt that there will always be a mismatch between neural field models and actual cortical tissue. Nevertheless, the simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data, that has the potential to influence the treatment of diseases such as epilepsy. The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.

@@

By assuming a linear activation function of the form
\begin{equation}
	f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}),
\end{equation}
the state transition equation~\eqref{eq:ApproxDiscreteTimeModel4} simplifies to
\begin{equation}\label{eq:ApproxDiscreteTimeModel_Linear}
	\mathbf{x}_{t+1} = 
	\xi \mathbf{x}_t + 
	\varsigma T_s \mathbf{\Lambda}_{x}^{-1} \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\int_\Omega { 
	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
	    \boldsymbol\mu^\top\left(\mathbf{r}'\right) 
	\, \mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}} \mathbf{x}_t
	+ \mathbf{w}_t.
\end{equation}
Now we can further simplify the system by defining
\begin{align}
	\label{eq:Lambdatheta}
	 \mathbf{\Lambda}_{\theta} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
		   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
		    \boldsymbol\mu^\top\left(r\right)\ \mathrm{d}r'\mathrm{d}r},
\end{align}
to give the state equation
\begin{equation}\label{eq:StateEquation}
 \mathbf x_{t+1} =\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t,
\end{equation} 
with the parameterized transition matrix
\begin{equation}\label{eq:A_theta}
 \mathbf A(\boldsymbol \theta)= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I.
\end{equation} 
The problem of joint state and parameter estimation for the state-space model given by Eq.~\eqref{eq:StateEquation} and Eq.~\eqref{eq:ReducedObservationEquation} can be formulated as 
\begin{equation}
	{\hat{\mathbf X},\hat{\boldsymbol\theta}}=\arg\max_{\mathbf X,\boldsymbol\theta}p(\mathbf Y;\boldsymbol\theta),
 \end{equation}  
where $\mathbf X$ and $\mathbf Y$ denote the entire sequences of the states and observations respectively, $\boldsymbol\theta$ is the parameter set and $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of the observations parameterized  by $\boldsymbol\theta$, known as the likelihood function. This dual estimation problem cannot be solved separately, as for the state estimation the knowledge of the system's parameters is required and for the parameter estimation the states of the system need to be known. One approach is to iteratively estimate the states and parameters of the system and monitor the convergence of the algorithm. A natural framework to perform this is the well known Expectation Maximization (EM) algorithm \citep{Dempster1977,Shumway2000} to infer both the parameter set and the states from the observations corresponding to the connectivity kernel, the neural field and electrophysiological data in our application. The EM algorithm is applicable  in two main situations:  first is when the observations are incomplete due to a faulty observation process or existing limitations and the second is when the direct maximization of the likelihood function is difficult but can be simplified by assuming the existence of an additional data referred to as hidden data \citep{Bilmes1998}, the weights of the field basis functions in this case. The EM algorithm, when used in the latter context \citep{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
\begin{equation}
	\boldsymbol\theta_{\text{ML}}=\arg\max_{\boldsymbol\theta}~p(\mathbf Y;\boldsymbol\theta),
 \end{equation}   
and the posterior distribution of the field over time.

@@

As mentioned earlier, the E-step for state-space models is equivalent to the smoothing problem. We use the RTS smoother, given in Table~\ref{alg:MRA-RTS} for completeness, in order to infer the states of the system. The RTS smoother uses the Kalman filter \citep{Kalman1960} in forward pass (Steps~1 and 2 in Table~\ref{alg:MRA-RTS}), along with a backward iteration to calculate its outputs (Steps~3 and 4 in Table~\ref{alg:MRA-RTS}): smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$. Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 in Table~\ref{alg:MRA-RTS})	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound to be maximized in the M-step. Note that the following quantities from the forward iteration should be stored when the RTS smoother is implemented: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$). Also, the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialize the backward cross-covariance computation. 

@@

@@

The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others~\citep{Wikle2002,Xu2005}. 
% \ken{meteorology [76, 88, 94, 222, 232], epidemiology [123, 137, 218], physics [32, 85, 129, 231], environmental science [45, 87, 183, 204] and economics [31, 48, 165]. (This is copy and paste from my thesis ... parham I'll get you the references later)}. \parham{Mike,Ken: can add to this list?}\mike{While I love this kind of thing for a review, I'm not sure we have space for this kind of thing? Also it's not terribly specific. I think it's better to stick to how it has the potential to model brains in a manner that rocks, rather than loosely saying it could be applied to any spatiotemporal system, i.e. literally everything.}

@@

% In order to apply the framework to real data some assumptions must be made. A critical assumption is that the model provides an apt description of the cortical dynamics.

To demonstrate MRAIDE framework, an assumption was made where the firing rate behaves linearly. The implementation of the framework in the nonlinear case can be addressed as future work. Another future avenue would be the modification of the estimation framework to perform efficiently at higher dimensions. The reconstruction of the neural field requires $2^n-1$ wavelets, where $n$ is the dimension of the space. For example a two-dimensional MRA can be implemented using 2-D scaling and wavelet functions built up using the tensor-product approach \citep{Meyer1992}. In this case three wavelet functions are required to  extract fine features of the field at vertical, horizontal and diagonal orientations. The formulations provided in this paper can be easily extended to two dimensions. However, the computational load of the estimation algorithm will be significant. It is important to investigate methods for choosing basis functions to balance the complexity with the reconstruction capability of the model.

The authors acknowledge that there is, and will always be, a discrepancy between the model and cortex. Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation. The key development is the multi-resolution decomposition forming the state-space model. While the decomposition holds for more sophisticated models, efficiently performing nonlinear smoothing in the large state-space remains a challenge.

Additional extension for future work include extending the model to capture a second order synaptic response kernel, The second-order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials. Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations. In small networks the delays via propagation can be neglected. However, delays must be accounted for in large scale networks. For instance, it is shown by \citet{Ghosh2008} that inclusion of time delays arising from propagation along connecting \parham{fibres} are essential for the fluctuations to be appeared in the default networks. Finally, future work should be directed towards applying and validating the framework on real data.

\newpage
\appendix
\section{Inner product of two B-spline scaling functions}\label{ap:InnerProductOfBsplines}
In this section, an analytic formula is derived for the inner product of two B-spline scaling functions. Consider two B-spline scaling functions of order $m$ and $m'$. The support of $N_m\left(s\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$, i.e.
\begin{align}\label{eq:APP-SymmetrySplieEq}
 N_{m}\left(\frac{m}{2}+r\right)=N_{m}\left(\frac{m}{2}-r\right).
\end{align}
A direct consequence of Eq.~\eqref{eq:APP-SymmetrySplieEq} is 
\begin{align}
 N_{m}\left(r\right)=N_{m}\left(m-r\right).
\end{align}
Therefore
\begin{align}
\int_{-\infty}^{+\infty}N_{m}\left(r-l_{1}\right)N_{m'}\left(r-l_{2}\right)dr&=\int_{-\infty}^{+\infty}N_{m}\left(m-r+l_{1}\right)N_{m'}\left(r-l_{2}\right)dr \nonumber \\
&=\int_{-\infty}^{+\infty}N_{m}\left(m+l_{1}-l_{2}-u\right)N_{m'}\left(u\right)du \nonumber \\
&=\left(N_m \ast N_{m'}\right) \left(m+l_{1}-l_{2}\right) \nonumber \\
&=N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
&=N_{m+m'}\left(m'+l_{2}-l_{1}\right).
\end{align}
\section{Scaling function expansion}\label{ap:Induction}  
In this appendix we show by induction that how the scaling function at $j=0$ can be written in terms of the scaling function at level $j$. For $n_1$ in  Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} we have
\begin{align}
 N_{m}\left(r\right)&=\sum_{n_1=0}^{m} \left[\mathbf p\right]_{n_1} N_{m}\left(2r-n_1\right) \label{eq:App-TwoScalepair1},
  \end{align}
which clearly holds from two-scale relation pair (see Eq.~\eqref{eq:MRA-TwoScalepair1}). Now assuming Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we can write 
\begin{align}\label{eq:app-ConvertingFormulaForscalingFunctions}
 &N_m(r)=\nonumber \\
&\sum_{n_1,n_2, \dots n_{j-1}=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_{j-1}}N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}}),
\end{align}
in which $N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})$ can be written in terms of $N_m(2^{j}r)$ as
\begin{align}\label{eq:AppendixNj-1intermsofNj}
 N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr-2\times k_{n_1,n_2, \dots, n_{j-1}}-n_j)\nonumber \\
&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr- k_{n_1,n_2, \dots, n_{j}}).
\end{align}
Substituting Eq.~\eqref{eq:AppendixNj-1intermsofNj} into Eq.~\eqref{eq:app-ConvertingFormulaForscalingFunctions} completes the proof.

>>>>

The multi-resolution approximation \citep{Mallat1989a} of the neural IDE (MRAIDE) is obtained by decomposing both the field, $v_t(\cdot)$, and the connectivity kernel, $w(\cdot)$, (assuming square-integrable functions) using translations and dilations of a scaling function $\phi(\mathbf{r})$ and a mother wavelet $\psi(\mathbf{r})$. Considering a  one-dimensional field, the static connectivity kernel is decomposed as,
\begin{equation}
 w\left(r\right)=\sum_{l\in \mathbb{Z}}\alpha_{j_0,l} \underbrace{\phi_{j_0,l}\left(r\right)}_{\text{scaling functions}} + \sum_{j\geq j_0}^{\infty} \sum_{l \in \mathbb{Z}}\beta_{j,l} \underbrace{\psi_{j,l}\left(r\right)}_{\text{wavelets}}, 
\label{eq:KernelExpansion}
\end{equation}
where $\alpha_{j_0,l}$ are the approximation coefficients at the lowest scale $j_0$, and $\beta_{j,l}$ are the detail coefficients at different scales $j$, with
\begin{align}
\phi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\phi\left(2^j r-l\right) \label{eq:generalscalingfinction}\\	
\psi_{j,l}\left(r\right) =& 2^{\frac{j}{2}}\psi\left(2^j r-l\right).  \label{eq:generalwaveletfinction}
\end{align}
The parameters $j$ and $l$ control the scale (dilation) and translation (spatial shift), respectively. The number of spatial shifts, $l$, is dependent on the scale, $j$, and can be chosen such that the basis functions cover the spatial domain of interest. For example, at scales corresponding to higher spatial frequencies a greater number of wavelets, and thus spatial shifts are required to adequately sample the spatial characteristics of the field. The number of scales depends on the spectral characteristics of the field, where higher spatial frequencies require  more scales. Spatial frequency analysis will be described later in Section~\ref{sec:freq_anal} in greater detail. Scaling functions retain the lowest frequency components, due to their low-pass properties, while the wavelet functions extract successively higher frequency components due to their band-pass characteristics.

@@

By exploiting Eqs.~\eqref{eq:BsplineConvolution} and \eqref{eq:BsplineInnerProduct}, the integrals in Eqs.~\eqref{eq:Lambdax} and \eqref{eq:Gammaij} can be computed analytically. In constructing $\boldsymbol\Lambda_{x}$, it is important to note that B-spline scaling and wavelet functions possess the following orthogonality properties \citep{Unser1993}: 
\begin{equation}
  \left\langle \varphi_{m;j_1,l_1}(r),\varphi_{m;j_2,l_2}(r)\right\rangle =0  \quad \mathrm{for} \quad j_1\neq j_2
 \label{eq:MRA-PsiPsiOrthogonality} 
 \end{equation}
 \begin{equation}
  \left\langle N_{m;j_1,l_1}(r),\varphi_{m;j_2,l_2}(r)\right\rangle =0  \quad \mathrm{for} \quad j_1\leq j_2.
 \label{eq:MRA-PhiPsiOrthogonality}
 \end{equation}
Note from Eq.~\eqref{eq:MRA-PsiPsiOrthogonality} B-spline wavelets are semi-orthogonal as they are not orthogonal with respect to translation on a given scale.

@@

It is important to point out there is no doubt that there will always be a mismatch between the model and actual cortical tissue. Nevertheless, the simplifications used in formulating the equations enable the development of new methods for extracting information from electrophysiological data, that has the potential to influence the treatment of diseases such as epilepsy. The trade-off between parsimony and complexity is always difficult when considering neurodynamics and this is further complicated when using estimation algorithms that have huge computational demands with such high-dimensional systems.

@@

By assuming a linear activation function of the form
\begin{equation}
	f(v_t(\mathbf{r})) = \varsigma v_t(\mathbf{r}),
\end{equation}
the state transition equation~\eqref{eq:ApproxDiscreteTimeModel4} simplifies to
\begin{equation}\label{eq:ApproxDiscreteTimeModel_Linear}
	\mathbf{x}_{t+1} = 
	\xi \mathbf{x}_t + 
	\varsigma T_s \mathbf{\Lambda}_{x}^{-1} \int_{\Omega}\boldsymbol\mu\left(\mathbf{r}\right)\int_\Omega { 
	    \boldsymbol\theta^\top\boldsymbol\lambda\left(\mathbf{r}-\mathbf{r}'\right)
	    \boldsymbol\mu^\top\left(\mathbf{r}'\right) 
	\, \mathrm{d}\mathbf{r}'\mathrm{d}\mathbf{r}} \mathbf{x}_t
	+ \mathbf{w}_t.
\end{equation}
Now we can further simplify the system by defining
\begin{align}
	\label{eq:Lambdatheta}
	 \mathbf{\Lambda}_{\theta} &\triangleq \int_{\Omega}\boldsymbol\mu\left(r\right) \int_\Omega { 
		   \boldsymbol\theta^\top\boldsymbol\lambda\left(r-r'\right)
		    \boldsymbol\mu^\top\left(r\right)\ \mathrm{d}r'\mathrm{d}r},
\end{align}
to give the state equation
\begin{equation}\label{eq:StateEquation}
 \mathbf x_{t+1} =\mathbf A(\boldsymbol \theta) \mathbf x_t+ \mathbf w_t,
\end{equation} 
with the parameterized transition matrix
\begin{equation}\label{eq:A_theta}
 \mathbf A(\boldsymbol \theta)= T_s\varsigma\mathbf{\Lambda}_{x}^{-1}\mathbf{\Lambda}_{\theta}+\xi\mathbf I.
\end{equation} 
The problem of joint state and parameter estimation for the state-space model given by Eq.~\eqref{eq:StateEquation} and Eq.~\eqref{eq:ReducedObservationEquation} can now be formulated as 
\begin{equation}
	{\hat{\mathbf X},\hat{\boldsymbol\theta}}=\arg\max_{\mathbf X,\boldsymbol\theta}p(\mathbf Y;\boldsymbol\theta),
 \end{equation}  
where $\mathbf X$ and $\mathbf Y$ denote the entire sequences of the states and observations respectively, $\boldsymbol\theta$ is the parameter set and $p(\mathbf Y;\boldsymbol\theta)$ denotes the probability density function of the observations parameterized  by $\boldsymbol\theta$, known as the likelihood function. This dual estimation problem cannot be solved separately, as for the state estimation the knowledge of the system's parameters is required and for the parameter estimation the states of the system need to be known. One approach is to iteratively estimate the states and parameters of the system and monitor the convergence of the algorithm. A natural framework to perform this is the well known Expectation Maximization (EM) algorithm \citep{Dempster1977,Shumway2000} to infer both the parameter set and the states from the observations corresponding to the connectivity kernel, the neural field and electrophysiological data in our application. The EM algorithm is applicable  in two main situations:  first is when the observations are incomplete due to a faulty observation process or existing limitations and the second is when the direct maximization of the likelihood function is difficult but can be simplified by assuming the existence of an additional data referred to as hidden data \citep{Bilmes1998}, the weights of the field basis functions in this case. The EM algorithm, when used in the latter context \citep{Dewar2009}, yields the maximum likelihood kernel estimate, i.e.
\begin{equation}
	\boldsymbol\theta_{\text{ML}}=\arg\max_{\boldsymbol\theta}~p(\mathbf Y;\boldsymbol\theta),
 \end{equation}   
and the posterior distribution of the field over time.

@@

As mentioned earlier, the E-step for state-space models is equivalent to the smoothing problem. We use the RTS smoother, given in Table~\ref{alg:MRA-RTS} for completeness, in order to infer the states of the system. The RTS smoother uses the Kalman filter \citep{Kalman1960} in forward pass (Steps~1 and 2 in Table~\ref{alg:MRA-RTS}), along with a backward iteration to calculate its outputs (Steps~3 and 4 in Table~\ref{alg:MRA-RTS}): smoothed states $\hat{\mathbf x}^b_t$ and covariances, $\mathbf P^b_t=\mathrm{cov}(\mathbf{x}_t)$. Following \cite{Gibsona2005}, an additional backwards recursion is also included (Step~5 in Table~\ref{alg:MRA-RTS})	to calculate cross-covariance matrix, $\mathbf M_t=\mathrm{cov}(\mathbf{x}_{t},\mathbf{x}_{t+1})$, which is also required in forming the lower bound on the likelihood function. Note that the following quantities from the forward iteration should be stored when the RTS smoother is implemented: predicted and corrected estimates for both state estimates ($\hat{\mathbf{x}}_t^{f-}$, $\hat{\mathbf{x}}_t^{f}$) and covariance matrices ($\mathbf P_t^{f-}$,$\mathbf P_t^f$). Also, the final value of the Kalman gain, $\mathcal K_T$, should be stored in order to initialize the backward cross-covariance computation. 

@@

\subsection{Estimation algorithm}

@@

@@

% In order to apply the framework to real data some assumptions must be made. A critical assumption is that the model provides an apt description of the cortical dynamics.
 \subsection{Modification to higher dimensions}
%To demonstrate MRAIDE framework, an assumption was made where the firing rate behaves linearly. The implementation of the framework in the nonlinear case can be addressed as future work. 
%Another future avenue would be the modification of the estimation framework to perform efficiently at higher dimensions.
 The reconstruction of the neural field in higher dimensions requires $2^n-1$ wavelets, where $n$ is the dimension of the space. For example a two-dimensional MRA can be implemented using 2-D scaling and wavelet functions built up using the tensor-product approach \citep{Meyer1992}. In this case three wavelet functions are required to  extract fine features of the field at vertical, horizontal and diagonal orientations. The formulations provided in this paper can be easily extended to two dimensions. However, the computational load of the estimation algorithm will be significant. It is important to investigate methods for choosing basis functions to balance the complexity with the reconstruction capability of the model.
\subsection{Extensions to the framework} 
The authors acknowledge that there is, and will always be, a discrepancy between the model and cortex. Nevertheless, the model-based framework proposed in this paper may enable meaningful state tracking and connectivity estimation. The MRAIDE approach is not limited to neural fields; the framework can be applied to modeling other multi-resolution spatiotemporal dynamical systems such as weather systems, ecological systems, and others~\citep{Wikle2002,Xu2005}. The key development is the multi-resolution decomposition forming the state-space model. While the decomposition holds for more sophisticated models, efficiently performing nonlinear smoothing in the large state-space remains a challenge.

Additional extension for future work include extending the model to capture a second order synaptic response kernel, The second-order postsynaptic kernel proposed in \citet{VanRotterdam1982} leads to dynamics that are more reminiscent to real postsynaptic potentials. Another extension of this framework is the inclusion of finite distant-dependent action potential propagation velocity into the parametric neural field equations. In small networks the delays via propagation can be neglected. However, delays must be accounted for in large scale networks. For instance, it is shown by \citet{Ghosh2008} that inclusion of time delays arising from propagation along connecting fibres are essential for the fluctuations to be appeared in the default networks. Finally, future work should be directed towards applying and validating the framework on real data.

\newpage
\appendix
\section{Inner product of two B-spline scaling functions}\label{ap:InnerProductOfBsplines}
In this section, an analytic formula is derived for the inner product of two B-spline scaling functions. Consider two B-spline scaling functions of order $m$ and $m'$. The support of $N_m\left(r\right)$ is $\left[ 0,m\right]$ and  is symmetric with respect to $r=\frac{m}{2}$, i.e.
\begin{align}\label{eq:APP-SymmetrySplieEq}
 N_{m}\left(\frac{m}{2}+r\right)=N_{m}\left(\frac{m}{2}-r\right).
\end{align}
A direct consequence of Eq.~\eqref{eq:APP-SymmetrySplieEq} is 
\begin{align}
 N_{m}\left(r\right)=N_{m}\left(m-r\right).
\end{align}
Therefore
\begin{align}
\int_{-\infty}^{+\infty}N_{m}\left(r-l_{1}\right)N_{m'}\left(r-l_{2}\right)dr&=\int_{-\infty}^{+\infty}N_{m}\left(m-r+l_{1}\right)N_{m'}\left(r-l_{2}\right)dr \nonumber \\
&=\int_{-\infty}^{+\infty}N_{m}\left(m+l_{1}-l_{2}-u\right)N_{m'}\left(u\right)du \nonumber \\
&=\left(N_m \ast N_{m'}\right) \left(m+l_{1}-l_{2}\right) \nonumber \\
&=N_{m+m'}\left(m+l_{1}-l_{2}\right) \nonumber \\
&=N_{m+m'}\left(m'+l_{2}-l_{1}\right).
\end{align}
\section{Scaling function expansion}\label{ap:Induction}  
In this appendix we show by induction that how the scaling function at $j=0$ can be written in terms of the scaling function at level $j$. For $n_1$ in  Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} we have
\begin{align}
 N_{m}\left(r\right)&=\sum_{n_1=0}^{m} \left[\mathbf p\right]_{n_1} N_{m}\left(2r-n_1\right) \label{eq:App-TwoScalepair1},
  \end{align}
which clearly holds from two-scale relation pair (see Eq.~\eqref{eq:MRA-TwoScalepair1}). Now assuming Eq.~\eqref{eq:MRA-ConvertingFormulaForscalingFunctions} for $n_{j-1}$ we can write 
\begin{align}\label{eq:app-ConvertingFormulaForscalingFunctions}
 &N_m(r)=\nonumber \\
&\sum_{n_1,n_2, \dots n_{j-1}=0}^{m}\left[\mathbf p\right]_{n_1} \left[\mathbf p\right]_{n_2}\dots \left[\mathbf p\right]_{n_{j-1}}N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}}),
\end{align}
in which $N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})$ can be written in terms of $N_m(2^{j}r)$ as
\begin{align}\label{eq:AppendixNj-1intermsofNj}
 N_m(2^{j-1}r-k_{n_1,n_2, \dots, n_{j-1}})&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr-2\times k_{n_1,n_2, \dots, n_{j-1}}-n_j)\nonumber \\
&=\sum_{n_j=0}^m \left[\mathbf p\right]_{n_j}N_m(2^jr- k_{n_1,n_2, \dots, n_{j}}).
\end{align}
Substituting Eq.~\eqref{eq:AppendixNj-1intermsofNj} into Eq.~\eqref{eq:app-ConvertingFormulaForscalingFunctions} completes the proof.
